\documentclass{resume} % Use the custom resume.cls style

%\documentclass{article}
\usepackage{hyperref}

\usepackage[left=0.3 in,top=0.4in,right=0.3 in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arkapratim Ghosh} % Name
% can merge both of these into a single line, if do not have a website.
\address{+91 9330450430 \\ Kolkata, India} 
\address{
  \href{mailto:arkapratimghosh1264@gmail.com}{arkapratimghosh1264@gmail.com} \\
  \href{https://www.linkedin.com/in/arkapratim-ghosh21102002/}{linkedin.com/arkapratim-ghosh21102002} \\
  \href{https://arkapg211002.github.io/}{Portfolio} \\
  \href{https://github.com/arkapg211002}{github.com/arkapg211002}
}
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech in Computer Science and Engineering}, {\bf{Techno Main Salt Lake}} {\bf (CGPA:} {\href{https://drive.google.com/drive/folders/186ArPQ8_JpwUQHSaDPuyN8eHIRixRpR9?usp=drive_link}{{\bf9.26}}}{\bf)} \hfill {2021 - 2025}\\
{\bf Relevant Courses:} Data Structures and Algorithms, Computer Organization and Architecture, Operating Systems, Object-Oriented Programming, Computer Networks, Database Management Systems, Distributed Systems, Microsoft Azure Fundamentals, AWS Cloud Practitioner.
%{\bf CGPA:} %{\href{https://drive.google.com/drive/folders/186ArPQ8_JpwUQHSaDPuyN8eHIRixRpR9?usp=drive_link}{{\bf9.26}}}

{\bf Council for Indian School Certificate Examinations, Pramila Memorial Institute} \\
{\bf ICSE:}  {\href{https://drive.google.com/file/d/1xUmXxrwusz0aJG7yyctvrCSJ8cQlLfuO/view?usp=drive_link}{{\bf 96.6\%}}} \hfill {2019}\ & & & & & & & & & & & & & & & & & & &
{\bf ISC:}  {\href{https://drive.google.com/file/d/1xR1JvYbxnG5Rm-GKsD8DwesRsmbV4UMW/view?usp=drive_link}{{\bf 94.75\%}}}\hfill {2021}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon 


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Core Java, C, Python, Swing, JavaFX, HTML, CSS, Bootstrap, Tailwind CSS, PHP, \\
& JavaScript, React, NodeJS, SQL, JDBC, MongoDB, Postman, Shell Scripting. \\

%& MySQL.
Software Tools & VS Code, Eclipse, Vim, Windows, Ubuntu, Github, Oracle Database XE 11g, XAMPP, \\ & StarUML, Dia, Docker, RapidMiner. \\
%Soft Skills & Communication, Problem Solving, Time Management, Creativity, %Adaptability. \\
Languages & English, Bengali, Hindi
\end{tabular}\
\end{rSection}

\begin{comment}

\begin{rSection}{EXPERIENCE}
\textbf{\href{https://www.cloudskillsboost.google/public_profiles/69d8b0de-6292-4dd9-8f83-288e6ea30dc9}{Google Cloud Ready Facilitator Program}} \textit{Google Cloud Education} \hfill April 2022 - June 2022 
\begin{itemize}
    \setlength\itemsep{-0.2em} % Reduce space between items
    \item Completed Track 1 and 2 covering cloud essentials, infrastructure and Google developer essentials.
    \item Explored Track 3 and 4 on Big Data, Machine Learning, Security, Machine Learning, and AI.
    \item Completed 3 milestones, earning a total of 34 quests and acquiring 18 skill badges.
\end{itemize}

\end{rSection}

    
\end{comment}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------



\begin{rSection}{PROJECTS}
    \vspace{-1.15em}
    
    \item \textbf{Personal Portfolio} {\href{https://arkapg211002.github.io/}{(Visit here)}} {\href{https://github.com/arkapg211002/arkapg211002.github.io}{[GitHub Repository]}}
    \begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Innovated a visually stunning portfolio using a combination of HTML5, CSS3, Bootstrap5, JavaScript, Typed.js for animated typing effects.
    \item Enacted functionality to open one terminal like a web page in another tab displaying personal details.
    \item Leveraged LocalStorage API to store the visitor’s preferred theme, which then takes effect on later visits.
    \item Utilized AOS animation v3.0.0 for smooth transitions and interactive tilting components using vanilla-tilt.js.
    \end{itemize}

    \item \textbf{Student Result Management System} {\href{https://arkaphpcrud.000webhostapp.com/index.php}{(Visit here)}}
    {\href{https://github.com/arkapg211002/Student-Result-Management-System}{[GitHub Repository]}}
    \begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Constructed one comprehensive software solution to streamline the management of student academic results.
    \item Executed HTML5, CSS3, Bootstrap5, JavaScript, jQuery, PHP8 to create a user friendly interface.
    \item Harnessed MySQL8 for handling and organizing academic data for more than 100 students within an institution.
    \item Put into effect features for real-time data management and analysis, ensuring efficient organization and accessibility of more than one academic record.
    \end{itemize}

    \item \textbf{PlayNet} {\href{https://play-net-eight.vercel.app/}{(Try it here)}}
    {\href{https://github.com/arkapg211002/PlayNet}{[GitHub Repository]}}
    \begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Created a YouTube clone web application using HTML5, CSS3, JavaScript, JSX (version  4.2),  ReactJS (version 18.0), and React Router DOM to offer users an immersive video browsing experience.
    \item Crafted the user interface of the application using Material UI, ensuring a polished and intuitive design.
    \item Integrated YouTube API v3 seamlessly from RapidApi into the application to provide users with  a smooth video browsing experience and enhanced content discovery capabilities.
    \item Conceptualized to emulate the fundamental features of YouTube, the application allows users to search for videos with rate-limited fetching of the latest 20 videos, ensuring familiarity and efficient browsing akin to the original platform.
    \end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
\setlength\itemsep{-1.75em} % Adjust the value as needed
     \item Successfully attained AZ-900 \href{https://learn.microsoft.com/en-in/users/arkapratimghosh-4932/credentials/certification-o-/azure-fundamentals}{certification} in Microsoft Azure with a \href{https://drive.google.com/file/d/1s7vbb-FW7VGSNXz2BCDkJnFmuanPQLEC/view}{score} of 700/814. \\
    \item   Ranked 9 among college mates on \href{https://www.geeksforgeeks.org/user/arkapratimghosh20021/?utm_source=geeksforgeeks&utm_medium=my_profile&utm_campaign=auth_user}{Geeks-For-Geeks}, reflecting programming proficiency. \\
    \item Demonstrated coding expertise with a rating of 1953 (Knight) and a global rank of 17401 on \href{https://leetcode.com/21Arka2002/}{LeetCode}. \\
    \item Attained \href{https://www.naukri.com/code360/profile/Arka2002}{Level 6 (Specialist)} status at code360, showcasing my proficiency in coding. \\
    \item Made \href{https://github.com/arkapg211002/TotalViewsProjectRepoReadme}{GitHub repositories} on assignments in college semesters that received more than 40000 views. \\
    \item Achieved a rank of 2993 in \href{https://drive.google.com/file/d/1xc6hvBjQhrxccVi4ENYZc62iL98IfvNh/view}{WBJEE} and an AIR (All India Rank) of 40316 in \href{https://drive.google.com/file/d/1xjdXfsoL_L62ij-P8jDuyyKQw9I1_Ht0/view}{JEE Main}.
\end{itemize}

% 

\end{rSection}




%----------------------------------------------------------------------------------------



\end{document}
