\documentclass{resume} % Use the custom resume.cls style

%\documentclass{article}
\usepackage{hyperref}

\usepackage[left=0.3 in,top=0.3in,right=0.3 in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arka Pratim Ghosh} % Name
% can merge both of these into a single line, if do not have a website.
\address{+91 9330450430 \\ Kolkata, India} 
\address{
  \href{mailto:arkapratimghosh1264@gmail.com}{arkapratimghosh1264@gmail.com} \\
  \href{https://www.linkedin.com/in/arkapratim-ghosh21102002/}{linkedin.com/arkapratim-ghosh21102002} \\
  \href{https://arkapg211002.github.io/}{Portfolio} \\
  \href{https://github.com/arkapg211002}{github.com/arkapg211002}
}
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech in Computer Science and Engineering}, {\bf{Techno Main Salt Lake}} {\bf (CGPA:} {\href{https://drive.google.com/drive/folders/186ArPQ8_JpwUQHSaDPuyN8eHIRixRpR9?usp=drive_link}{{\bf9.26}}}{\bf)} \hfill{09/2021 - 06/2025}\\
{\bf Relevant Courses:} Data Structures and Algorithms, Computer Organization and Architecture, Operating Systems, Object-Oriented Programming, Computer Networks, Database Management Systems, Distributed Systems, Microsoft Azure Fundamentals, AWS Cloud Practitioner.
%{\bf CGPA:} %{\href{https://drive.google.com/drive/folders/186ArPQ8_JpwUQHSaDPuyN8eHIRixRpR9?usp=drive_link}{{\bf9.26}}}

{\bf Council for Indian School Certificate Examinations, Pramila Memorial Institute} \\
{\bf ISC:}  {\href{https://drive.google.com/file/d/1xR1JvYbxnG5Rm-GKsD8DwesRsmbV4UMW/view?usp=drive_link}{{\bf 94.75\%}}}\hfill {07/2021}\ & & & & & & & & & & & & & & & & & & &
{\bf ICSE:}  {\href{https://drive.google.com/file/d/1xUmXxrwusz0aJG7yyctvrCSJ8cQlLfuO/view?usp=drive_link}{{\bf 96.6\%}}} \hfill {05/2019}

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon 


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Core Java, C, Python, Swing, JavaFX, HTML, CSS, Bootstrap, Tailwind CSS, PHP, \\
& JavaScript, React, NodeJS, SQL, JDBC, MongoDB, Postman, Shell Scripting. \\

%& MySQL.
Software Tools & VS Code, Eclipse, Vim, Windows, Ubuntu, GitHub, Oracle Database XE 11g, XAMPP, \\ & StarUML, Dia, Docker, RapidMiner. \\
%Soft Skills & Communication, Problem Solving, Time Management, Creativity, %Adaptability. \\
Languages & English, Bengali, Hindi.
\end{tabular}\
\end{rSection}

%\begin{comment}

\begin{rSection}{EXPERIENCE}
\textbf{\href{https://drive.google.com/drive/folders/1zJUxf5e83R8e-LNZSDJIef5HuBml4bJN?usp=drive_link}{Altair Data Science Master Virtual Internship}} \textit{Eduskills} \hfill 05/2024 - 06/2024 
\vspace{-0.6em}
\begin{itemize}
    \setlength\itemsep{-0.6em} % Reduce space between items
    \item Fulfilled the internship, adeptly utilizing RapidMiner for data processing across one main dataset.
    \item Mastered Track 3 and 4 on Data Engineering and Machine Learning covering the basics.
    \item Accomplished 7 certification exams on topics covering basics, data engineering, machine learning, and activities as platform administrator in RapidMiner.
\end{itemize}

\end{rSection}

    
%\end{comment}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------



\begin{rSection}{PROJECTS}
   \vspace{-1.00em}

      % Changed Personal Portfolio Project
     \item \textbf{Personal Portfolio Website
    {\href{https://arkapg211002.github.io/}{(Visit here)}}
    {\href{https://github.com/arkapg211002/arkapg211002.github.io}{[GitHub Repository]}} :} 
    \vspace{-0.6em}
    \begin{itemize}
    \setlength\itemsep{-0.6em}
    \item Launched a visually stunning portfolio using a combination of HTML5, CSS3, Bootstrap5, JavaScript, Typed.js for animated typing effects.
    \item Addressed functionality to open terminal web page in another browser and utilized LocalStorage API to store visitor’s preferred theme for later visits.
    \item Incorporated AOS animation v3.0.0 for smooth transitions, tilting components using vanilla tilt JavaScript library.
    \end{itemize}
    
    \item \textbf{Student Result Management System 
    {\href{https://arkapratimghoshsrms13000121058.000webhostapp.com/index.php}{(Visit here)}}
    {\href{https://github.com/arkapg211002/Student-Result-Management-System}{[GitHub Repository]}} :}
    \vspace{-0.6em}
    \begin{itemize}
    \setlength\itemsep{-0.6em}
     \item Spearheaded one comprehensive software solution to streamline the management of student academic results.
    \item Executed HTML5, CSS3, Bootstrap5, JavaScript, jQuery, PHP8, and MySQL8 to create a robust project for handling and organizing academic data for more than 100 students within an educational institution.
    \item Administered effective features for real-time data management and analysis, ensuring efficient organization and accessibility of more than one academic record.
    \end{itemize}
    
    % Changed Playnet Project
    \item \textbf{PlayNet (Video Streaming Web Application)
    {\href{https://play-net-eight.vercel.app/}{(Visit here)}}
    {\href{https://github.com/arkapg211002/PlayNet}{[GitHub Repository]}} :} 
    \vspace{-0.6em}
    \begin{itemize}
    \setlength\itemsep{-0.6em}
     \item Introduced  a  YouTube  clone  web  application  using  HTML5,  CSS3,  JavaScript,  JSX  (version  4.2),  ReactJS (version 18.0), and React Router DOM to offer users an immersive video browsing experience.
    \item Revamped the user interface of the application using Material UI, ensuring one polished and intuitive design.
    \item Integrated  YouTube  API  v3  seamlessly from RapidApi and coordinated usage into  the  application  to  provide  users  with  a  smooth  video  browsing experience and 100\% up-time content discovery capabilities.
    \item Designed  to  emulate  the  fundamental  features  of  YouTube,  the  application  allows  users  to  search  for  videos with rate-limited fetching of the latest 20 videos, ensuring familiarity and efficient browsing akin to the original platform.
    \end{itemize}
    

  
\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
\setlength\itemsep{-1.75em} % Adjust the value as needed
     \item Achieved AZ-900 (Azure Fundamentals) \href{https://learn.microsoft.com/en-in/users/arkapratimghosh-4932/credentials/certification-o-/azure-fundamentals}{certification} in Microsoft Azure with a \href{https://drive.google.com/file/d/1s7vbb-FW7VGSNXz2BCDkJnFmuanPQLEC/view}{score} of 814. \\
    \item   Ranked 9 among college mates on \href{https://www.geeksforgeeks.org/user/arkapratimghosh20021/?utm_source=geeksforgeeks&utm_medium=my_profile&utm_campaign=auth_user}{Geeks-For-Geeks}, reflecting programming proficiency. \\
    \item Demonstrated coding expertise with a rating of 1953 (Knight) and a global rank of 17401 on \href{https://leetcode.com/21Arka2002/}{LeetCode}. \\
   % \item Attained \href{https://www.naukri.com/code360/profile/Arka2002}{Level 6 (Specialist)} status at code360, showcasing my proficiency in coding. \\
    \item Composed \href{https://github.com/arkapg211002/TotalViewsProjectRepoReadme}{GitHub repositories} on assignments in college semesters that received more than 40000 views. \\
    \item Achieved a rank of 2993 in \href{https://drive.google.com/file/d/1xc6hvBjQhrxccVi4ENYZc62iL98IfvNh/view}{WBJEE} and an AIR (All India Rank) of 40316 in \href{https://drive.google.com/file/d/1xjdXfsoL_L62ij-P8jDuyyKQw9I1_Ht0/view}{JEE Main}.
\end{itemize}

% 

\end{rSection}




%----------------------------------------------------------------------------------------



\end{document}
