I am writing to express my interest in the technical consultant role at IBM(International Business Machines), as advertised. With a strong academic background in Computer Science and Engineering from Techno Main Salt Lake and a wealth of practical experience in software development and cloud technologies, I am excited about the opportunity to contribute to your team.

During my studies, I have honed my skills in a wide array of programming languages and technologies including Java, Python, React, NodeJS, SQL, and more. This technical foundation has been complemented by hands-on projects, such as developing a visually captivating personal portfolio website and implementing a Student Result Management System using a range of technologies including HTML, CSS, Bootstrap, JavaScript, PHP, and MySQL.

One of my proudest achievements is obtaining the Microsoft Azure Fundamentals certification (AZ-900) with a commendable score, underscoring my commitment to continuous learning and staying abreast of industry trends. Additionally, my contributions on platforms like Geeks-For-Geeks and LeetCode highlight my strong problem-solving abilities and programming proficiency.

I am particularly drawn to IBM(International Business Machines) due to its reputation for innovation and problem-solving through cutting-edge technologies. The prospect of working as a technical consultant excites me as it aligns perfectly with my passion for leveraging technology to address complex challenges faced by clients across diverse industries. I am eager to apply my analytical mindset and communication skills to deliver impact solutions and enhance client experiences.

Enclosed is my resume, which provides further detail on my qualifications. I would welcome the opportunity to discuss how my background, skills, and enthusiasm for technology can contribute to the success of IBM(International Business Machines). Thank you for considering my application. I look forward to the possibility of contributing to your team.
